G\"odel's God in Isabelle/HOL

### 2013-11-08 Formalizations/Isabelle/ScottsVersion/output/document/root.tex
Reorganize folders

\noindent\fcolorbox{gray}{white}{
\begin{minipage}{.96\textwidth}\small
\begin{itemize}
\item[A1] Either a property or its negation is positive, but not
  both:  \hfill 
  $\all \phi [P(\neg \phi) \biimp \neg P(\phi)]$ \\[-1.5em]
\item[A2] A property necessarily implied \\ by a
  positive property is positive: \phantom{b} \hfill 
  $\all \phi \all \psi [(P(\phi) \wedge \nec \all x [\phi(x)
  \imp \psi(x)]) \imp P(\psi)]$ \\[-1.5em]
\item[T1] Positive properties are possibly exemplified: \hfill $\all
  \varphi [P(\varphi) \imp \pos \ex x \varphi(x)]$ \\[-1.5em]
\item[D1] A \emph{God-like} being possesses all positive properties: \hfill
  $G(x) \biimp \forall \phi [P(\phi) \to \phi(x)]$ \\[-1.5em]
\item[A3]  The property of being God-like is positive: \hfill   $P(G)$ \\[-1.5em]
\item[C\phantom{1}] Possibly, God exists: \hfill $\pos \ex x G(x)$ \\[-1.5em]
\item[A4]  Positive properties are necessarily positive: \hfill 
  $\all \phi [P(\phi) \to \Box \; P(\phi)]$ \\[-1.5em]
\item[D2] An \emph{essence} of an individual is a property possessed by it \\ and necessarily implying any of its properties:
  \phantom{b} \hfill $\ess{\phi}{x} \biimp \phi(x) \wedge \all
  \psi (\psi(x) \imp \nec \all y (\phi(y) \imp \psi(y)))$ \\[-1.5em]
\item[T2]  Being God-like is an essence of any
  God-like being: \hfill $\all x [G(x) \imp \ess{G}{x}]$ \\[-1.5em]
\item[D3] \emph{Necessary existence} of an individual is \\ the necessary exemplification of all its essences: 
  \phantom{b} \hfill $\NE(x) \biimp \all \phi [\ess{\phi}{x} \imp \nec
  \ex y \phi(y)]$ \\[-1.5em]
\item[A5] Necessary existence is a positive property: \hfill $P(\NE)$ \\[-1.5em]
\item[T3] Necessarily, God exists: \hfill $\nec \ex x G(x)$ 
\end{itemize}
\end{minipage}
}
\vskip1em

@@

\paragraph{Acknowledgments:} Nik Sultana, Jasmin Blanchette and Larry Paulson provided 
very important help wrt consistency checking in Isabelle. Jasmin Blanchette instructed us on how to 
produce latex documents from Isabelle sources, and he showed us useful tricks in Isabelle.

>>>>

\noindent\fcolorbox{gray}{white}{
\begin{minipage}{.96\textwidth}\small
\begin{itemize}
\item[A1] Either a property or its negation is positive, but not
  both:  \hfill 
  $\all \phi [P(\neg \phi) \biimp \neg P(\phi)]$ \\[-1.5em]
\item[A2] A property necessarily implied \\ by a
  positive property is positive: \phantom{b} \hfill 
  $\all \phi \all \psi [(P(\phi) \wedge \nec \all x [\phi(x)
  \imp \psi(x)]) \imp P(\psi)]$ \\[-1.5em]
\item[T1] Positive properties are possibly exemplified: \hfill $\all
  \varphi [P(\varphi) \imp \pos \ex x \varphi(x)]$ \\[-1.5em]
\item[D1] A \emph{God-like} being possesses all positive properties: \hfill
  $G(x) \biimp \forall \phi [P(\phi) \to \phi(x)]$ \\[-1.5em]
\item[A3]  The property of being God-like is positive: \hfill   $P(G)$ \\[-1.5em]
\item[C\phantom{1}] Possibly, God exists: \hfill $\pos \ex x G(x)$ \\[-1.5em]
\item[A4]  Positive properties are necessarily positive: \hfill 
  $\all \phi [P(\phi) \to \Box \; P(\phi)]$ \\[-1.5em]
\item[D2] An \emph{essence} of an individual is a property possessed by it \\ and necessarily implying any of its properties: \\
  \phantom{b} \hfill $\ess{\phi}{x} \biimp \phi(x) \wedge \all
  \psi (\psi(x) \imp \nec \all y (\phi(y) \imp \psi(y)))$ \\[-1.5em]
\item[T2]  Being God-like is an essence of any
  God-like being: \hfill $\all x [G(x) \imp \ess{G}{x}]$ \\[-1.5em]
\item[D3] \emph{Necessary existence} of an individual is \\ the necessary exemplification of all its essences: 
  \phantom{b} \hfill $\NE(x) \biimp \all \phi [\ess{\phi}{x} \imp \nec
  \ex y \phi(y)]$ \\[-1.5em]
\item[A5] Necessary existence is a positive property: \hfill $P(\NE)$ \\[-1.5em]
\item[T3] Necessarily, God exists: \hfill $\nec \ex x G(x)$ 
\end{itemize}
\end{minipage}
}
\vskip1em

@@

\paragraph{Acknowledgments:} Nik Sultana, Jasmin Blanchette and Larry Paulson provided 
very important help on issues related to consistency checking in Isabelle. Jasmin Blanchette instructed us on how to 
produce latex documents from Isabelle sources and showed us useful tricks in Isabelle.
